% Cole Greenlee Resume

% Document Setup
\documentclass[letterpaper,11pt]{article}



% Packages used in this resume
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[sfdefault]{roboto}

% Document Setup
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\renewcommand{\labelitemii}{$\vcenter{\hbox{\tiny$\bullet$}}$}
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}
\titleformat{\section}{\vspace{-4pt}\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
% This is **critical** in optimising this document for ATS parsing
\input{glyphtounicode}
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{\item\small{{#1 \vspace{-2pt}}}}
\newcommand{\techSkillItem}[2]{\item{\small{\textbf{#1: }{#2}}}\vspace{-5pt}}
\newcommand{\techSkillList}[1]{\begin{itemize}[leftmargin=0.15in]#1\end{itemize}\vspace{-15pt}}
\newcommand{\blogLinkItem}[3]{\item{\begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}\href{#2}{\textit{``#1``} \small{\faLink}} & \small{#3}\end{tabular*}\vspace{-2pt}}}
\newcommand{\blogLinkList}[1]{\begin{itemize}[leftmargin=0.15in]#1\end{itemize}\vspace{-5pt}}
\newcommand{\resumeSection}[2]{\section{#1}\begin{itemize}[leftmargin=0.15in, label={}]#2\end{itemize}}
\newcommand{\resumeItemHeading}[4]{\vspace{-2pt}\item{\begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}\textbf{#1} & #2\\\textit{\small#3} & \textit{\small #4}\\\end{tabular*}\vspace{-7pt}}}
\newcommand{\resumeProjectHeading}[2]{\item{\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}\small#1 & #2 \\ \end{tabular*}\vspace{-7pt}}}
\newcommand{\resumeItemList}[1]{\begin{itemize}#1\end{itemize}\vspace{-5pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% Begin Resume Document
\begin{document}

% Title
\begin{center}
	\begin{small}
		\textbf{\Huge \scshape Cole Greenlee} \\ \vspace{5pt}
		\href{https://Greenlee.io/}{\faGlobe/Greenlee.io}  $|$
		\href{mailto:Cole@Greenlee.io}{\faEnvelope[regular]/Cole@Greenlee.io} $|$
		\href{https://LinkedIn.com/in/ColeGreenlee}{\faLinkedin/ColeGreenlee} $|$
		\href{https://GitHub.com/ColeGreenlee}{\faGithub/ColeGreenlee}
	\end{small}
\end{center}

% Education
\resumeSection{Education}{
	\resumeItemHeading{University of Minnesota - Twin Cities}{Minneapolis, MN}{Bachelor of Applied Sciences: Information Technology Infrastructure - DevOps Focus}{Aug. 2018 -- Present}
}

% Technical Proficiencies
\section{Technical Proficiencies}
\techSkillList{
	\techSkillItem{Languages}{Java, Groovy, C\#, Python, C, JavaScript, TypeScript, HTML, CSS, R}
	\techSkillItem{Frameworks}{Angular, React, .NET MVC, Django, Flask}
	\techSkillItem{Databases}{MSSQL, MySQL, PostgreSQL, MongoDB}
	\techSkillItem{Tools}{Git, Docker, Jenkins CI/CD, AWS, JIRA}
}

% Professional Experience
\resumeSection{Professional Experience}{
	\resumeItemHeading{Software Engineer Intern}{Jan. 2020 -- Present}{Infinite Campus}{Blaine, MN}
	\resumeItemList{
		\resumeItem{Developed new features in Angular applications used for financial reporting in 2,000 school districts in 45 states.}
		\resumeItem{Created new REST API endpoints and features using the Spring framework.}
		\resumeItem{Implemented endpoint unit testing with Groovy and Spock to validate financial reports.}
		\resumeItem{Trained new intern team members in company's tech stack and development practices.}
	}

	\resumeItemHeading{Software Developer}{Sep. 2020 -- Present}{Pulse Reporting Inc.}{Remote}
	\resumeItemList{
		\resumeItem{Lead a startup company's web application development efforts using Angular.}
		\resumeItem{Developed a REST API service using the Djano Rest Framework}
		\resumeItem{Guided team members in creating and maintaining a public data web scraper integral to company operations.}
		\resumeItem{Integrated geographic API services for mapping and weather data from corporate partners.}
		\resumeItem{Developed deployment pipeline for AWS using ECS, ELB, and RDS cloud services.}
	}

	\resumeItemHeading{Software Developer \& Remote Team Manager}{Jun. 2015 -- Jan. 2020}{Innovative Computer Professionals Inc.}{Prior Lake, MN}
	\resumeItemList{
		\resumeItem{Developed a multi-institution financial application for credit card issuing, company payroll, and customer support in .NET.}
		\resumeItem{Designed an ATM and payment processor monitoring system in Java for servers operating on a global scale.}
		\resumeItem{Obtained OWASP Top 10 Certification in compliance with company’s PCI DSS Certification.}
		\resumeItem{Independently managed and planned delivery schedules for company’s offshore UI development team.}
		\resumeItem{Designed, updated, and deployed a collection of customer and company websites.}
		\resumeItem{Wrote technical documentation for company API service endpoints.}
	}
}

% Projects
\resumeSection{Projects}{
	\resumeProjectHeading{\textbf{Blog} $|$ \emph{Authored writeups on a myriad of technical topics}}{Jan. 2022 -- Present}
	\blogLinkList{
		% Test Post List - Need to replace with real posts
		\blogLinkItem{Creating an Automated Static Site with Hugo}{https://greenlee.io/posts/creating-an-automated-hugo-site/}{12/10/2021}
		\blogLinkItem{Building ATS-Safe LaTeX Resumes}{https://greenlee.io/posts/building-an-ats-safe-latex-resume/}{01/10/2022}
		\blogLinkItem{100 Days of LeetCode - A Retrospectice}{https://greenlee.io/posts/100-days-of-leetcode-retrospective/}{02/01/2022}
		\blogLinkItem{Planning a Project: Before the Code}{https://greenlee.io/posts/planning-a-project-before-the-code/}{02/03/2022}
	}

	\resumeProjectHeading{\textbf{HomeLab} $|$ \emph{My Infrastructure as Code Respository}}{Mar. 2018 -- Present}
	\resumeItemList{
		\resumeItem{Automated server configuration using Ansible.}
		\resumeItem{Configured deployment stacks using containerized applications.}
		\resumeItem{Worked to standardize deployment configuration process.}
	}
}
\end{document}